Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-20 talk_ucl_cdt_200622/adaptive.tex
QASS theory slide

\begin{frame}
	\frametitle{The QASS Algorithm}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

@@

% TODO Graham: add some more slides here depending on your preferences

>>>>

\begin{frame}
	\frametitle{Adaptive Sampling: Theory}
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-6cm-5mm}

        Adaptive sampling takes advantage of surrogate information content \textit{during training} to reduce sample quantity.\newline

        We developed a technique which is novel in the literature:
        \begin{itemize}
        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
        \item Draw candidate samples by quality using MCMC.
        \item Include samples with high crowding distance.
        \item Repeat!
        \end{itemize}
      \column{6cm}
      \includegraphics[width=8cm]{qassplan}

    \end{columns}
\end{frame}

@@

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
QASS theory slide

        These runs included full evaluations on the 18 continuous discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.

>>>>

        These runs included full evaluations on the 18 continuous and discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.
